
\begin{itemize}
\item Explain the meaning of $F$ and $f$. 
\item Hoe bepaal je $F$ adhv data? Geef een voorbeeld.
\item Hoe moet je de vergelijking $S_r(r) = F(r)$ lezen? Studenten lezen het als een gelijkheid, maar ze weten niet dat $S_r(r)$ het ding is dat je wil weten, en dat $F(r)$ de data/het gegeven is, en dat je dus de fill rate kan uitdrukken in data die je al weet. 
\item Leg formules uit in tekst, net als Ross.
\item Wat triggert een bestelling, voorraadpositie of voorraadlevel. Studenten snappen het verschil niet.
\item Do we charge for $\IP$ or for $\IL$? So, which of the two should appear in the cost functions?
\item In cycle service level, moeten we nemen $\P{I_i > 0}$ of $P(I_i\geq 0}$?
\end{itemize}

\section{todo}
\label{sec:todo}




\begin{itemize}
\item Bring laptop to the first tutorial
\item Check steps for the tutorial as mentioned in the slides of Jan.
\item Check questions on the slides of Jan.
\item include sections to read, of e.g., think stats, in the notes.
\item How do our 4 stages and LP formulations fit together? Demand is
  data, cost in the objective, production and item characteristics in
  the constraints, policy choice is decision variable.
\end{itemize}


find a good place for this insight: Modeling errors have, typically, much more influence on the
reliability of the insights that errors in data estimations. Realize
that the world is pretty complex \ldots TBD.


\section{Organization}
\label{sec:organization}


lecture 1, why inventories?

\begin{enumerate}
\item demostrate approach in excel
\end{enumerate}

2:demand characterization
\begin{enumerate}
\item newsvendor model
\item give demand profile, cdf, pmf, distribution fitting, (log)normal distribution
\item show that profit for the newsvendor is not very sensitive to
  forecast errors, value of perfect info is not super high. 
\item KPI's to determine the quality of the demand forecast: MSE, RMSE\ldots
\item demand forecasting is not a goal per se,
\item moving average, exp smooth
\item holt winters
\item demand during leadtime, leadtime variability, $\sigma^2 = l d + d^2 \sigma_L^2$.
\item Intermittend demand and compound Poisson
\item autoregression?
\item autocorrelation function
\item Graphical analysis of the quality of the forecast.
\item Can demand be backlogged or not? Lost or not, partially lost?
  How long can it be backlogged? How to prevent backlogging and loss
  (with building up inventories)
\end{enumerate}

3: Characteristics of Production, ordering, and items.
\begin{enumerate}
\item EOQ, epq
\item quantity discounts
\item lot sizing
\item basestock
\item q,r model
\item s,S 
\item LP formulations
\item multi-item
\item ABC characterization
\item Ordering strategies
\item Period/continous time review.
\item Impact of bucksize, choice of review period length in case of periodic review.
\item Should the ordering moments coincide with the review moments?
\item Perishability? 
\item inventory loss due to theft and so on?
\item yield loss?
\item Power of 2 ordering interval.
\end{enumerate}

4: cost characterization, KPI's
\begin{itemize}
\item make  trade-offs clear and explicit.
\item OTIF
\item How to evaluate the (relevance of the) quality of the demand and cost data? 
\end{itemize}


5: policy choice and optimization
\begin{enumerate}
\item How to choose a control policy?
\item How to optimize it?  Determine good policy parameters
\item Sensitivity analysis
\item Robustness
\item Tuning of holt-winters demand parameters?
\end{enumerate}

6: reviewing an article


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
